---
title: "functions"
author: "Saksham"
date: "2023-07-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ETAS.inlabru)
library(ggplot2)

# Increase/decrease num.cores if you have more/fewer cores on your computer.
# future::multisession works on both Windows, MacOS, and Linux
num.cores <- 6
future::plan(future::multisession, workers = num.cores)
INLA::inla.setOption(num.threads = num.cores)
# To deactivate parallelism, run
#   future::plan(future::sequential)
#   INLA::inla.setOption(num.threads = 1)
```

## Set up the transformations

```{r}
# set copula transformations list
link.f <- list(
  mu = \(x) gamma_t(x, 0.3, 0.6),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)

# set inverse copula transformations list
inv.link.f <- list(
  mu = \(x) inv_gamma_t(x, 0.3, 0.6),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)
```

## Data Preprocessing

```{r}
# transform time string in Date object
horus$time_date <- as.POSIXct(
  horus$time_string,
  format = "%Y-%m-%dT%H:%M:%OS"
)
# There may be some incorrectly registered data-times in the original data set,
# that as.POSIXct() can't convert, depending on the system.
# These should ideally be corrected, but for now, we just remove the rows that
# couldn't be converted.
horus <- na.omit(horus)

# set up parameters for selection
start.date <- as.POSIXct("2009-01-01T00:00:00", format = "%Y-%m-%dT%H:%M:%OS")
end.date <- as.POSIXct("2010-01-01T00:00:00", format = "%Y-%m-%dT%H:%M:%OS")
min.longitude <- 10.5
max.longitude <- 16
min.latitude <- 40.5
max.latitude <- 45
M0 <- 2.5

# set up conditions for selection
aquila.sel <- (horus$time_date >= start.date) &
  (horus$time_date < end.date) &
  (horus$lon >= min.longitude) &
  (horus$lon <= max.longitude) &
  (horus$lat >= min.latitude) &
  (horus$lat <= max.latitude) &
  (horus$M >= M0)

# select
aquila <- horus[aquila.sel, ]
```

```{r}
ggplot(aquila, aes(time_date, M)) +
  geom_point() +
  theme_bw()
```

```{r}
# set up data.frame for model fitting
aquila.bru <- data.frame(
  ts = as.numeric(
    difftime(aquila$time_date, start.date, units = "days")
  ),
  magnitudes = aquila$M,
  idx.p = 1:nrow(aquila)
)
```

## set up the initial values

```{r}
# set up list of initial values
th.init <- list(
  th.mu = inv.link.f$mu(0.5),
  th.K = inv.link.f$K(0.1),
  th.alpha = inv.link.f$alpha(1),
  th.c = inv.link.f$c_(0.1),
  th.p = inv.link.f$p(1.1)
)
```

## set the list of inlabru options

```{r}
# set up list of bru options
bru.opt.list <- list(
  bru_verbose = 3, # type of visual output
  bru_max_iter = 70, # maximum number of iterations
  # bru_method = list(max_step = 0.5),
  bru_initial = th.init # parameters' initial values
)
```

## function to fit the model

```{r}
model_fit <- function(full_data,
                      magnitude,
                      start_time,
                      end_time,
                      link_functions,
                      bru_options_list){
  aquila.fit <- Temporal.ETAS(
  total.data = full_data,
  M0 = magnitude,
  T1 = start_time,
  T2 = end_time,
  link.functions = link_functions,
  coef.t. = 1,
  delta.t. = 0.1,
  N.max. = 5,
  bru.opt = bru_options_list
  )
  return(aquila.fit)
}
```

### fit the model

```{r}
T1 <- 0
T2 <- max(aquila.bru$ts) + 0.2 # Use max(..., na.rm = TRUE) if there may still be NAs here
horus_data_fit <- model_fit(full_data=aquila.bru,
                            magnitude = M0,
                            start_time = T1,
                            end_time = T2,
                            link_functions = link.f,
                            bru_options_list = bru.opt.list)
```

## function to generate input list

```{r}

get_input_list <- function(fitted_model,
                           link_functions)
  {
  # create input list to explore model output
  input_list <- list(
    model.fit = fitted_model,
    link.functions = link_functions
  )
  return(input_list)
}

horus_input_list <- get_input_list(horus_data_fit,
                                   link.f)
```

##function to check posterior marginal distributions

```{r}
marg_posterior <- function(input_list,
                           num.cores){
  # get marginal posterior information
  post.list <- get_posterior_param(input.list = input_list)
  
  # plot marginal posteriors
  post.list$post.plot
}
```

## function to get a posterior sample

```{r}
get_post_sample <- function(input_list){
  #now get a posterior sample
  post.samp <- post_sampling(
  input.list = input_list,
  n.samp = 1000,
  max.batch = 1000,
  ncore = num.cores
  )
  
  return(post.samp)
}
```

function to plot pair plots

```{r}
pair_plots_plotter <- function(post_sample){
  pair.plot <- post_pairs_plot(
  post.samp = post_sample,
  input.list = NULL,
  n.samp = NULL,
  max.batch = 1000
  )
  pair.plot$pair.plot
}
```


```{r}
#checking posterior marginals, getting  posterior samples and plottting pair plots
marg_posterior(input_list = horus_input_list,num.cores = num.cores )
horus_post_sample <- get_post_sample(horus_input_list)
pair_plots_plotter(post_sample = horus_post_sample)
```

## function to check posterior number of events

```{r}
check_posterior_events <- function(input_list,
                                   full_data,
                                   start_time,
                                   end_time,
                                   magnitude){
  # set additional elements of the list
  input_list$T12 <- c(start_time, end_time)
  input_list$M0 <- magnitude
  input_list$catalog.bru <- full_data
  N.post <- get_posterior_N(input.list = input_list)
  my_plot <- N.post$post.plot
  return(list(input_list = input_list,
         my_plot = my_plot))
}
```

```{r}
result <- check_posterior_events(input_list = horus_input_list,
                                 full_data = aquila.bru,
                                 start_time = T1,
                                 end_time = T2,
                                 magnitude = M0) 

result$my_plot
horus_input_list <- result$input_list
```

```{r}
# plot_function <- function(input_list,post.samp){
#   triggering_fun_plot(
#   input.list = input_list,
#   post.samp = post.samp,
#   n.samp = NULL, magnitude = 4,
#   t.end = 5, n.breaks = 100
#   )
#   triggering_fun_plot_prior(input.list = input_list, magnitude = 4, 
#                             n.samp = 1000, t.end = 10)
#   omori_plot_posterior(input.list = input_list, post.samp = post.samp, 
#                        n.samp = NULL, t.end = 5)
#   omori_plot_prior(input.list = input_list, n.samp = 1000, t.end = 5)
# }
# 
# plot_function(input_list = horus_input_list,
#               post.samp = horus_post_sample)
```

## function to generate synthetic catalogues

```{r}
generate_synthetic_data <- function(post.samp,
                                    beta.p,
                                    magnitude,
                                    start_time,
                                    end_time,
                                    Ht){
  synth.cat.list <- generate_temporal_ETAS_synthetic(
  theta = post.samp[1, ], # ETAS parameters
  beta.p = beta.p, # magnitude distribution parameter
  M0 = magnitude, # cutoff magnitude
  T1 = start_time, # starting time
  T2 = end_time, # end time
  Ht = Ht # known events
  )
  # merge into unique data.frame
  synth.cat.df <- do.call(rbind, synth.cat.list)
  # order events by time
  synth.cat.df <- synth.cat.df[order(synth.cat.df$ts), ]
  return(synth.cat.df)
}
```

## generating first synthetic data

```{r}
beta.p <- 1 / (mean(aquila.bru$magnitudes) - M0)
synthetic_data_1 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )
```

```{r}
library(cluster)
#Function to get the optimal number of clusters
count_clusters <- function(full_data){
  
  data_for_clustering <- full_data[, c("ts", "magnitudes")]
  
  # Prepare a range of possible cluster numbers
  k_values <- 2:10
  
  # Initialize an empty vector to store the within-cluster sum of squares (WCSS)
  awss <- vector("numeric", length(k_values))
  
  # Calculate AWSS for each value of k
  for (i in seq_along(k_values)) {
    kmeans_result <- kmeans(data_for_clustering, centers = k_values[i])
    awss[i] <- mean(kmeans_result$withinss)
  }
  
  # Calculate the relative change in WSS for each value of k
  relative_change_wss <- numeric(length(awss) - 1)
  for (i in 2:length(awss)) {
    relative_change_wss[i - 1] <- (awss[i - 1] - awss[i]) / awss[i - 1] * 100
  }
  
  # Set the threshold for relative change in WSS to determine the optimal number of clusters
  threshold <- 10  # You can adjust this threshold as needed
  
  # Plot the elbow curve
  plot(k_values, awss, 
       type = "b", pch = 19,
       frame = FALSE,
       xlab = "Number of Clusters (k)",
       ylab = "Average Within-Cluster Sum of Squares (AWSS)")
  
  # Identify the optimal number of clusters based on the threshold
  optimal_k <- k_values[which.max(relative_change_wss <= threshold)]
  
  # Identify the "elbow" point using some threshold (you can adjust this threshold as needed)
  # elbow_point <- k_values[which(diff(awss) < mean(diff(awss)))[1]]
  
  # Print the identified optimal number of clusters
  # cat("Optimal number of clusters:", elbow_point, "\n")
  # return(elbow_point)
  return (optimal_k)
}
```

```{r}

quantify_data_characteristics <- function(full_data){
  main_earthquakes <- sum(full_data$magnitude > 4.5)
  clusters <- count_clusters(full_data = full_data)
  return(list(main_earthquakes = main_earthquakes,
              clusters = clusters))
}

```

```{r}

characteristics_synthetic_data_1 <- quantify_data_characteristics(full_data = 
                                                                    synthetic_data_1)
```

```{r}
characteristics_synthetic_data_1$clusters
```

```{r}
synthetic_data_1 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )
```

```{r}
nrow(synthetic_data_1)
```

## fit model on the firs synthetic data

```{r}
horus_post_estimates <- apply(horus_post_sample, 2, mean) 
```

```{r}
horus_post_estimates
```

### set the new priors

```{r}
synthetic_data_1_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) gamma_t(x, 0.3, 0.6),
  alpha = \(x) unif_t(x, 2.4381, 2.4383),
  c_ = \(x) gamma_t(x, 0.3, 0.6),
  p = \(x) unif_t(x, 1, 10)
)
```

### fit the model

```{r}
synthetic_data_1_fit <- model_fit(full_data=synthetic_data_1,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_1_priors,
                                  bru_options_list = bru.opt.list)
```

### get posterior plots

```{r}
#checking posterior marginals, getting  posterior samples and plotting pair plots
synthetic_data_1_input_list <- get_input_list(synthetic_data_1_fit,
                                   synthetic_data_1_priors)

marg_posterior(input_list = synthetic_data_1_input_list,
               num.cores = num.cores )
synthetic_data_1_post_sample <- get_post_sample(synthetic_data_1_input_list)
pair_plots_plotter(post_sample = synthetic_data_1_post_sample)
```

```{r}
synthetic_data_1_post_estimates <- apply(synthetic_data_1_post_sample, 2, mean) 
synthetic_data_1_post_estimates
```

```{r}
horus_post_estimates
```

```{r}
X <- rnorm(1000)
gamma.X <- gamma_t(X,100,0.01)
df.to.plot <- data.frame(
    value = gamma.X,
    distribution = "Gamma"
  )
ggplot(df.to.plot, aes(value)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(facets = ~distribution, scales = "free")

```

## fit second model

### generate second sample

```{r}
synthetic_data_2 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )
```

```{r}
synthetic_data_2_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) gamma_t(x, 0.3, 0.6),
  alpha = \(x) unif_t(x, 2.4381, 2.4383),
  c_ = \(x) gamma_t(x, 0.3, 0.6),
  p = \(x) unif_t(x, 1.177007, 1.177009)
)
```

```{r}
synthetic_data_2_fit <- model_fit(full_data=synthetic_data_2,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_2_priors,
                                  bru_options_list = bru.opt.list)
```

### get posteriors

```{r}
synthetic_data_2_input_list <- get_input_list(synthetic_data_2_fit,
                                   synthetic_data_2_priors)

marg_posterior(input_list = synthetic_data_2_input_list,
               num.cores = num.cores )
synthetic_data_2_post_sample <- get_post_sample(synthetic_data_2_input_list)
pair_plots_plotter(post_sample = synthetic_data_2_post_sample)
```

### get posterior estimates

```{r}
synthetic_data_2_post_estimates <- apply(synthetic_data_2_post_sample, 2, mean) 
synthetic_data_2_post_estimates
```

```{r}
horus_post_estimates
```

It is observed that on fixing 3 parameters- mu, alpha and p, our model is able to closely estimate the true parameters.

Now let's see which parameter leads to better estimates of

## fit the third model

### set the prior

we will take the case when we know all of our parameters

```{r}
synthetic_data_3_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) unif_t(x, 0.13751, 0.13753),
  alpha = \(x) gamma_t(x, 0.3, 0.6),
  c_ = \(x) unif_t(x, 0.070039, 0.07005),
  p = \(x) unif_t(x, 1.177008, 1.1770089)
)
```

###generate the dataset

```{r}
synthetic_data_3 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )
```

### fit the model

```{r}
synthetic_data_3_fit <- model_fit(full_data=synthetic_data_3,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_3_priors,
                                  bru_options_list = bru.opt.list)
```

### get posteriors

```{r}
#checking posterior marginals, getting  posterior samples and plotting pair plots
synthetic_data_3_input_list <- get_input_list(synthetic_data_3_fit,
                                   synthetic_data_3_priors)

marg_posterior(input_list = synthetic_data_3_input_list,
               num.cores = num.cores )
synthetic_data_3_post_sample <- get_post_sample(synthetic_data_3_input_list)
pair_plots_plotter(post_sample = synthetic_data_3_post_sample)
```

### get posterior estimates

```{r}
synthetic_data_3_post_estimates <- apply(synthetic_data_3_post_sample, 2, mean) 
synthetic_data_3_post_estimates
```

```{r}
horus_post_estimates
```

WE can clearly see that the estimate of alpha is very close to its true value

## fir fourth model

this time we consider mu and alpha both to be unknown. let's see what happens

### set the priors

```{r}
synthetic_data_4_priors <- list(
  mu = \(x) gamma_t(x, 0.3, 0.6),
  K = \(x) unif_t(x, 0.13751, 0.13753),
  alpha = \(x) gamma_t(x, 0.3, 0.6),
  c_ = \(x) unif_t(x, 0.070039, 0.07005),
  p = \(x) unif_t(x, 1.177008, 1.1770089)
)
```

### generate the synthetic dataset

```{r}
synthetic_data_4 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )
```

### fit the model

```{r}
synthetic_data_4_fit <- model_fit(full_data=synthetic_data_4,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_4_priors,
                                  bru_options_list = bru.opt.list)
```

### get posteriors

```{r}
#checking posterior marginals, getting  posterior samples and plotting pair plots
synthetic_data_4_input_list <- get_input_list(synthetic_data_4_fit,
                                   synthetic_data_4_priors)

marg_posterior(input_list = synthetic_data_4_input_list,
               num.cores = num.cores )
synthetic_data_4_post_sample <- get_post_sample(synthetic_data_4_input_list)
pair_plots_plotter(post_sample = synthetic_data_4_post_sample)
```

```{r}
synthetic_data_4_post_estimates <- apply(synthetic_data_4_post_sample, 2, mean) 
synthetic_data_4_post_estimates
```

```{r}
horus_post_estimates
```

we see that the posterior estimate of alpha obtained is close to its true value but the estimate of Mu not that close

## fit the fifth model

Now we will take the case where p is unknown along with alpha

```{r}
synthetic_data_5_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) unif_t(x, 0.13751, 0.13753),
  alpha = \(x) gamma_t(x, 0.3, 0.6), ## unknown
  c_ = \(x) unif_t(x, 0.070039, 0.07005), 
  p = \(x) unif_t(x, 1, 10) ## unknown
)

synthetic_data_5 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )

synthetic_data_5_fit <- model_fit(full_data=synthetic_data_5,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_5_priors,
                                  bru_options_list = bru.opt.list)

synthetic_data_5_input_list <- get_input_list(synthetic_data_5_fit,
                                   synthetic_data_5_priors)

marg_posterior(input_list = synthetic_data_5_input_list,
               num.cores = num.cores )
synthetic_data_5_post_sample <- get_post_sample(synthetic_data_5_input_list)
pair_plots_plotter(post_sample = synthetic_data_5_post_sample)

```

```{r}
synthetic_data_5_post_estimates <- apply(synthetic_data_5_post_sample,2,mean)
synthetic_data_5_post_estimates
```

```{r}
horus_post_estimates
```

This time we observe that neither alpha nor p was estimated correctly

## fit the sixth model

In this model we will assume that mu and c are unknown

```{r}
synthetic_data_6_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) unif_t(x, 0.13751, 0.13753),
  alpha = \(x) gamma_t(x, 0.3, 0.6), ## unknown
  c_ = \(x) gamma_t(x, 0.3, 0.6), ##unknown
  p = \(x) unif_t(x, 1.177008, 1.1770089)
)

synthetic_data_6 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )

synthetic_data_6_fit <- model_fit(full_data=synthetic_data_6,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_6_priors,
                                  bru_options_list = bru.opt.list)

synthetic_data_6_input_list <- get_input_list(synthetic_data_6_fit,
                                   synthetic_data_6_priors)

marg_posterior(input_list = synthetic_data_6_input_list,
               num.cores = num.cores )
synthetic_data_6_post_sample <- get_post_sample(synthetic_data_6_input_list)
pair_plots_plotter(post_sample = synthetic_data_6_post_sample)
```

```{r}
synthetic_data_6_post_estimates <- apply(synthetic_data_6_post_sample,2,mean)
synthetic_data_6_post_estimates
```

```{r}
horus_post_estimates
```

The same thing happens, we get a close estimate of alpha but not of c

## fit the seventh model

this time we will assume K and alpha to be unknown

```{r}
synthetic_data_7_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) gamma_t(x,0.3,0.6),
  alpha = \(x) gamma_t(x, 0.3, 0.6), ## unknown
  c_ = \(x) unif_t(x, 0.070039, 0.07005), 
  p = \(x) unif_t(x, 1.177008, 1.1770089)
)

synthetic_data_7 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )

synthetic_data_7_fit <- model_fit(full_data=synthetic_data_7,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_7_priors,
                                  bru_options_list = bru.opt.list)

synthetic_data_7_input_list <- get_input_list(synthetic_data_7_fit,
                                   synthetic_data_7_priors)

marg_posterior(input_list = synthetic_data_7_input_list,
               num.cores = num.cores )
synthetic_data_7_post_sample <- get_post_sample(synthetic_data_7_input_list)
pair_plots_plotter(post_sample = synthetic_data_7_post_sample)
```

```{r}
synthetic_data_7_post_estimates <- apply(synthetic_data_7_post_sample,2,mean) 
synthetic_data_7_post_estimates
```

```{r}
horus_post_estimates
```

## We see that the estimate of alpha is very accurate for all cases except for the one where p is missing

## fit the eighth model

SO lets take a case where every parameter is missing except for p

```{r}
synthetic_data_8_priors <- list(
  mu = \(x) gamma_t(x, 0.3, 0.6),
  K = \(x) gamma_t(x,0.3,0.6),
  alpha = \(x) gamma_t(x, 0.3, 0.6), ## unknown
  c_ = \(x) gamma_t(x, 0.3, 0.6), 
  p = \(x) unif_t(x, 1.177008, 1.1770089)
)

synthetic_data_8 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )

synthetic_data_8_fit <- model_fit(full_data=synthetic_data_8,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_8_priors,
                                  bru_options_list = bru.opt.list)

synthetic_data_8_input_list <- get_input_list(synthetic_data_8_fit,
                                   synthetic_data_8_priors)

marg_posterior(input_list = synthetic_data_8_input_list,
               num.cores = num.cores )
synthetic_data_8_post_sample <- get_post_sample(synthetic_data_8_input_list)
pair_plots_plotter(post_sample = synthetic_data_8_post_sample)
```

```{r}
synthetic_data_8_post_estimates <- apply(synthetic_data_8_post_sample,2,mean)
synthetic_data_8_post_estimates
```

```{r}
horus_post_estimates
```

We observe that even though there is only parameter known i.e p, we are still able to get good estimates of the other parameters present in our model

Lets check if this would be true, if oue other estimates are missing too

```{r}
synthetic_data_9_priors <- list(
  mu = \(x) gamma_t(x, 0.3, 0.6),
  K = \(x) gamma_t(x,0.3,0.6),
  alpha = \(x) gamma_t(x, 0.3, 0.6), ## unknown
  c_ = \(x) unif_t(x, 0.070039, 0.07005), 
  p = \(x) gamma_t(x, 0.3, 0.6)
)

synthetic_data_9 <- generate_synthetic_data(post.samp = horus_post_sample,
                                            beta.p = beta.p,
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            Ht = NULL
                                            )

synthetic_data_9_fit <- model_fit(full_data=synthetic_data_9,
                                  magnitude = M0,
                                  start_time = T1,
                                  end_time = T2,
                                  link_functions = synthetic_data_9_priors,
                                  bru_options_list = bru.opt.list)

synthetic_data_9_input_list <- get_input_list(synthetic_data_9_fit,
                                   synthetic_data_9_priors)

marg_posterior(input_list = synthetic_data_9_input_list,
               num.cores = num.cores)
synthetic_data_9_post_sample <- get_post_sample(synthetic_data_9_input_list)
pair_plots_plotter(post_sample = synthetic_data_9_post_sample)
```

```{r}
synthetic_data_9_post_estimates <- apply(synthetic_data_9_post_sample,2,mean)
synthetic_data_9_post_estimates
```

```{r}
horus_post_estimates
```

```{r}
synthetic_data_1_priors <- list(
  mu = \(x) unif_t(x, 0.30096, 0.30098),
  K = \(x) gamma_t(x, 0.3, 0.6),
  alpha = \(x) unif_t(x, 2.4381, 2.4383),
  c_ = \(x) gamma_t(x, 0.3, 0.6),
  p = \(x) unif_t(x, 1, 10)
)

# Set the number of iterations
num_iterations <- 5

# Loop through the iterations
for (i in 1:num_iterations) {
  # Create variable names dynamically using paste
  synthetic_data_set_1_data_name <- paste("synthetic_data_", i, sep = "")
  synthetic_data_fit_set_1_data_name <- paste("synthetic_data_", i, "_fit", sep = "")
  synthetic_data_input_list_set_1_data_name <- paste("synthetic_data_", i, "_input_list", sep = "")
  synthetic_data_post_sample_set_1_data_name <- paste("synthetic_data_", i, "_post_sample", sep = "")
  
  # Perform the process for each iteration with dynamically generated variable names
  assign(synthetic_data_set_1_data_name, generate_synthetic_data(post.samp = horus_post_sample,
                                                     beta.p = beta.p,
                                                     magnitude = M0,
                                                     start_time = T1,
                                                     end_time = T2,
                                                     Ht = NULL))

  assign(synthetic_data_fit_set_1_data_name, model_fit(full_data = get(synthetic_data_set_1_data_name),
                                            magnitude = M0,
                                            start_time = T1,
                                            end_time = T2,
                                            link_functions = synthetic_data_1_priors,
                                            bru_options_list = bru.opt.list))

  assign(synthetic_data_input_list_set_1_data_name, get_input_list(get(synthetic_data_fit_set_1_data_name),
                                                        synthetic_data_1_priors))

  marg_posterior(input_list = get(synthetic_data_input_list_set_1_data_name),
                 num.cores = num.cores)

  assign(synthetic_data_post_sample_set_1_data_name, get_post_sample(get(synthetic_data_input_list_set_1_data_name)))

  pair_plots_plotter(post_sample = get(synthetic_data_post_sample_set_1_data_name))
}

```

```{r}
```

```{r}
```

```{r}
```

```{r}
```

```{r}
```
